---
title: "Exploratory Data Analysis of Airbnb Prices in Paris, France"
subtitle: "My subtitle if needed"
author: 
  - Talia Fabregas
thanks: "Code and data are available at: https://github.com/taliafabs/ParisAirbnb.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

# token: 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
library(janitor)
library(arrow)
library(knitr)
library(ggplot2)
library(readr)
paris_airbnb_data_selected <- read_parquet("2023-12-12-paris-airbnblistings-select_variables.parquet")
```


# Introduction

Exploratory Data Analysis is the process of exploring and familiarizing ourselves with a dataset @tellingstorieswithdata. There is no one-size-fits-all exploratory data analysis process. Instead, there is a common goal: to gain a general idea of the story that a dataset might be able to tell.

In this paper, I examined Airbnb listings in Paris, France, as of December 12, 2023. I will conduct exploratory data analysis similar to the example shown in Telling Stories with Data Chapter 11.5 @tellingstorieswithdata. I am interested in understanding the distribution of Airbnb prices in Paris, the relationships between variables such as whether or not the host is a super host and the average price per night of an Airbnb, and exploring what data is missing, why it is missing, what part of the story it contributes to, and how I can handle the missing data appropriately.


I used @citer, @tellingstorieswithdata, @citeggplot, @citearrow @airbnbdata,


# Data {#sec-data}

The data that I used is from Inside Airbnb @airbnbdata. I selected the city of Paris, France, and downloaded the December 12, 2023 detailed listings data. The original data set does not belong to me, therefore I've used a ".gitignore" to prevent it from being pushed onto GitHub.

The data set contains many variables, however, I have selected 12 to use.  host_id, host_response_time, host_is_superhost, host_total_listings_count, neighbourhood_cleansed, bathrooms, bedrooms, price, number_of_reviews, review_scores_rating, review_scores_accuracy, and review_scores_value for my exploratory data analysis. In order to filter the data set to only include the 12 variables I selected, I used @janitor and the select function as part of my data cleaning process.


# Exploratory Data Analysis {#sec-eda}

## Prices Per Night
Someone who is considering traveling to Paris might be interested in how much accomodations might cost. The first part of my exploratory data analysis will involve examining the distribution of Paris Airbnb prices per night. I started by looking at the overall distribution of Airbnb prices per night in @distn_prices. 

```{r}
#| label: fig-distn_prices
#| fig-cap: Distribution of Prices per Night 
#| echo: false

paris_airbnb_data_selected |>
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 10) +
  theme_classic() +
  labs(
    x = "Price per night",
    y = "Number of properties"
  )
```


```{r}
#| label: fig-over_1000_logscale
#| fig-cap: Prices over $1000 using log scale
#| echo: false
#| warning: false
#| message: false

paris_airbnb_data_over_1000 <- paris_airbnb_data_selected |>
  filter(price > 1000)

paris_airbnb_data_over_1000 |>
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 10) +
  theme_classic() +
  labs(
    x = "Price per night",
    y = "Number of properties"
  ) +
  scale_y_log10()
```


## Prices under 1000
Most people planning a trip to Paris are probably looking for an Airbnb that costs less than $1000 per night. 
```{r}
#| label: fig-under1000
#| fig-cap: Prices under $1000
#| echo: false
#| warning: false
#| message: false

paris_airbnb_data_below_1000 <- paris_airbnb_data_selected |>
  filter(price < 1000)

paris_airbnb_data_cheap <-paris_airbnb_data_selected |>
  filter(price > 90) |>
  filter(price < 210) 

paris_airbnb_data_below_1000 |>
  filter(price < 1000) |>
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 10) +
  theme_classic() +
  labs(
    x = "Price per night",
    y = "Number of properties"
  )

# price per night between 90 and 210
paris_airbnb_data_cheap |>
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 1) +
  theme_classic() +
  labs(
    x = "Price per night",
    y = "Number of properties"
  )
```


## Superhosts Versus Non-Superhosts for Airbnb Listings Below $1000

Superhosts are experienced Airbnb hosts @tellingstorieswithdata. As part of my exploratory data analysis process, I am interested in gaining a general understanding of how prices and review scores vary between superhosts and non-superhosts. 

```{r}
#| label: fig-reviewscores
#| fig-cap: Prices under $1000
#| echo: false
#| warning: false
#| message: false
superhost_na <- paris_airbnb_data_below_1000 |>
  filter(is.na(host_is_superhost))

paris_airbnb_data_superhost <- paris_airbnb_data_below_1000 |>
  filter(!is.na(host_is_superhost)) |>
  mutate(
    host_is_superhost_binary = as.numeric(host_is_superhost)
  )

paris_airbnb_data_superhost |>
  ggplot(aes(x = review_scores_rating)) +
  geom_bar() +
  theme_classic() +
  labs(
    x = "Review scores rating",
    y = "Number of properties"
  )
```
To explore the possibility of a relationship between super host status and price per night in Airbnbs in the <$1000 price range, I am examining the mean airbnb price per night where the host is a superhost versus when the host is not a superhost.

```{r}
# we want to see the mean price for superhosts and non-superhosts
superhosts <- paris_airbnb_data_superhost |>
  filter(host_is_superhost_binary == 1)

non_superhosts <- paris_airbnb_data_superhost |>
  filter(host_is_superhost_binary == 0)

mean_table <- data.frame(
  superhost_mean_price = mean(superhosts$price),
  non_superhost_mean_price = mean(non_superhosts$price)
)

kable(mean_table)
```
# Results

Our results are summarized in






# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


